### 2020-04-23 reports/thesis/book.tex
typo

\begin{titlingpage}
\centering
{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications to Additive Manufacturing \par}
\vspace{1cm}
{\Large Sherman Edea Lo\par}
{\Large Doctor of Philosophy in Statistics\par}
\vfill
\includegraphics[width = 0.75\textwidth]{../figures/frontCover.jpg}
\vfill
{\Large University of Warwick\par}
{\Large Department of Statistics\par}
{\Large May 2020\par}
\end{titlingpage}

@@

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were investigated and it was discuused how they were handled. In Chapter \ref{chapter2}, a test sample was additively manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic error in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, novel statistical techniques were developed and implemented to look for defects in the test sample in the face of uncertainty. This was done by comparing the experimental projection with a simulated projection and looking for any disagreement. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

@@

This thesis is a contribution to real-time quality control for AM and perhaps inverse problems in imaging \citep{bertero1998introduction} and robust statistics. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. This could be competitive with other converyor belt inspection methods, for example \cite{warnett2016towards}, by using less projections and hopefully less computational time. By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of AM.

>>>>

\begin{titlingpage}
\centering
{\LARGE Characterisation of Computed Tomography Noise in Projection Space with Applications to Additive Manufacturing \par}
\vspace{1cm}
{\Large Sherman Edea Lo\par}
{\Large Doctor of Philosophy in Statistics\par}
\vfill
\includegraphics[width = 0.75\textwidth]{../figures/frontCover.jpg}
\vfill
{\Large University of Warwick\par}
{\Large Department of Statistics\par}
{\Large April 2020\par}
\end{titlingpage}

@@

In Chapter \ref{chapter1}, x-ray computed tomography and additive manufacturing is reviewed. Sources of error were investigated and it was discussed how they were handled. In Chapter \ref{chapter2}, a test sample was additively manufactured and the chapter describes how experimental x-ray projections were obtained. Shading correction is explained here and it was used to remove sources of systematic error in the projections. In Chapter \ref{chapter3}, the compound Poisson distribution is studied so that it can be used to model the detection of x-rays. In Chapter \ref{chapter4}, the uncertainty in the projection was quantified using the variance and generalised linear models were used to predict it. In Chapter \ref{chapter5}, novel statistical techniques were developed and implemented to look for defects in the test sample in the face of uncertainty. This was done by comparing the experimental projection with a simulated projection and looking for any disagreement. The empirical null filter was used to cater for any model misspecification so that sensible conclusions were made. The thesis ends with an evaluation in Chapter \ref{chapter6}.

@@

This thesis is a contribution to real-time quality control for AM and perhaps inverse problems in imaging \citep{bertero1998introduction} and robust statistics. A powerful multi-core computer could be used to conduct the statistical analysis on a few x-ray projections of AM products on a conveyor belt. This could be competitive with other conveyor belt inspection methods, for example \cite{warnett2016towards}, by using fewer projections and hopefully less computational time. By using fewer projections, quality control can be faster which advances the development and increases the scope of applications of AM.
